---
title: "capstone data analysis - creative"
format: html
editor: visual
---

### RUN DATA CLEANING QMD FIRST PLS

```{r setup and data import}
 
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(broom)
library(janitor)
library(skimr)
library(tinytex)
library(writexl)
library(pillar)
library(knitr)
library(scales)
library(DT)

dat_kpis <- read_csv("data/dat_kpis.csv")
```

```{r increase display size}
# tl;dr show more data on one screen
# increase the number of columns printed on screen
options(pillar.width = Inf) # try to use full width of document
options(pillar.max_footer_lines = 3) # allows more lines in the footer if columns are truncated
```

## Data Glossary

Here's an explanation of each column in the final `dat_kpis` dataset:

### Original & Cleaned Location Columns

-   **`location`**: The original, raw location string as it appeared in the input data (e.g., "Orlando-Daytona Beach, Florida", "Mobile, Alabama-Pensacola, Florida").
-   **`city`**: The city part extracted directly after splitting the location string by the first comma. This might contain multiple city names or DMA names (e.g., "Orlando-Daytona Beach", "Champaign & Springfield-Decatur").
-   **`state`**: The cleaned and standardized state name, corrected for cross-state DMA entries (e.g., "Florida", "Alabama", "Tennessee").
-   **`city_primary`**: The single, primary city name extracted from the `city` column, intended for geocoding and mapping (e.g., "Orlando", "Champaign", "Mobile", "Los Angeles").
-   **`state_raw`**: A temporary column holding the state information immediately after the initial separate split, before manual corrections were applied (e.g., "Florida", "Alabama-Pensacola, Florida").

### Ad Details & Targeting Columns

-   **`audience_segment`**: Describes the target audience characteristics or online behavior used for showing the ad (e.g., "Online Behavior\>United States\>Finance\>Financial Planning...").
-   **`creative_size`**: The dimensions of the ad creative in pixels (e.g., "300x250", "320x50").
-   **`creative_messaging`**: The marketing message or call to action used in the ad (e.g., "Subscribe Today - 10% Discount", "Sign up Now - 10% Off").
-   **`app_url`**: The specific website or app where the ad impression occurred (e.g., "accuweather.com", "cnn.com").
-   **`exchange`**: The advertising technology platform that facilitated the ad serving (e.g., "Google Ad Manager", "PubMatic").
-   **`device_make`**: The type of device on which the ad was displayed (e.g., "Smartphone", "Apple PC", "Windows PC").

### Core Performance Metrics

-   **`impressions`**: The total number of times the ad was displayed.
-   **`clicks`**: The total number of times the ad was clicked.
-   **`viewable_impressions`**: The number of impressions where the ad met industry standards for actually being considered viewable by a user.
-   **`measurable_impressions`**: The number of impressions for which viewability could be technically measured.
-   **`total_conversions`**: The number of times a desired action (like a sign-up or purchase) was completed after a user clicked the ad.
-   **`gross_cost`**: The total amount spent for the ad impressions/clicks listed in that row.

### Calculated KPIs

-   **`ctr` (Click-Through Rate)**: $(\frac{\text{clicks}}{\text{impressions}})$. Shows the percentage of impressions that led to a click.
-   **`conv_rate` (Conversion Rate)**: $(\frac{\text{total\_conversions}}{\text{clicks}})$. Shows the percentage of clicks that led to a conversion.
-   **`cpa` (Cost Per Acquisition)**: $(\frac{\text{gross\_cost}}{\text{total\_conversions}})$. The average cost to acquire one conversion. ($\text{NA}$ if conversions $\text{= 0}$).
-   **`cpc` (Cost Per Click)**: $(\frac{\text{gross\_cost}}{\text{clicks}})$. The average cost for each click. ($\text{NA}$ if clicks $\text{= 0}$).
-   **`ecpm` (Effective Cost Per Mille/Thousand)**: $(\frac{\text{gross\_cost}}{\text{impressions}}) \times 1000$. The cost for one thousand impressions.
-   **`view_rate` (Viewability Rate)**: $(\frac{\text{viewable\_impressions}}{\text{measurable\_impressions}})$. The percentage of measurable impressions that were actually viewable.
-   **`vcpm` (Viewable Cost Per Mille/Thousand)**: $(\frac{\text{gross\_cost}}{\text{viewable\_impressions}}) \times 1000$. The cost for one thousand viewable impressions. ($\text{NA}$ if viewable_impressions $\text{= 0}$).

# accidentally did creative analyst stuff! work is here

# Creative Analyst Stuff/Exploring Additional Insights Beyond Location

## Analyze performance by app/website where ad appeared

```{r analyze app_url exchange - data summary check}
dat_kpis |> 
  select(impressions) |> 
  skim()
```

```{r analyze app_url exchange - data}
# analyze performance by the website/app where the ad appeared
# performance per app/url
app_performance <- dat_kpis |>
  group_by(app_url) |>
  summarise(
    total_impressions = sum(impressions),
    total_clicks = sum(clicks),
    total_conversions = sum(total_conversions),
    total_gross_cost = sum(gross_cost),
    avg_cpa = ifelse(total_conversions > 0, total_gross_cost / total_conversions, na_real_),
    avg_ctr = ifelse(total_impressions > 0, total_clicks / total_impressions, 0),
    .groups = 'drop'
  ) |>
  # focus on sites with a decent number of impressions to make stats more stable
  filter(total_impressions > 14024.5) |>
  # sort by cost-effectiveness (lowest cpa)
  arrange(avg_cpa)

# performance per exchange
exchange_performance <- dat_kpis |>
  group_by(exchange) |>
  summarise(
    total_impressions = sum(impressions),
    total_clicks = sum(clicks),
    total_conversions = sum(total_conversions),
    total_gross_cost = sum(gross_cost),
    avg_cpa = ifelse(total_conversions > 0, total_gross_cost / total_conversions, na_real_),
    avg_ctr = ifelse(total_impressions > 0, total_clicks / total_impressions, 0),
    .groups = 'drop'
  ) |>
  # sort by total conversions first, then by cpa
  arrange(desc(total_conversions), avg_cpa)
```

```{r analyze app_url exchange, results = 'asis'}
# store top/bottom apps
top_apps <- head(app_performance, 15)
bottom_apps <- tail(app_performance, 15)

# helper function to format these tables
format_app_table <- function(table_data) {
  table_data |>
    mutate(
      total_impressions = scales::comma(total_impressions, accuracy = 1),
      total_clicks = scales::comma(total_clicks, accuracy = 1),
      total_conversions = scales::comma(total_conversions, accuracy = 1),
      total_gross_cost = scales::dollar(total_gross_cost, accuracy = 0.01),
      avg_cpa = scales::dollar(avg_cpa, accuracy = 0.01),
      avg_ctr = scales::percent(avg_ctr, accuracy = 0.01)
    ) |>
    kable(format = "html",
          col.names = c("app/url", "total impressions", "total clicks", "total conversions", "total cost", "avg cpa", "avg ctr"))
}

# helper function for exchange table
format_exchange_table <- function(table_data) {
  table_data |>
    mutate(
      total_impressions = scales::comma(total_impressions, accuracy = 1),
      total_clicks = scales::comma(total_clicks, accuracy = 1),
      total_conversions = scales::comma(total_conversions, accuracy = 1),
      total_gross_cost = scales::dollar(total_gross_cost, accuracy = 0.01),
      avg_cpa = scales::dollar(avg_cpa, accuracy = 0.01),
      avg_ctr = scales::percent(avg_ctr, accuracy = 0.01)
    ) |>
    kable(format = "html",
          col.names = c("exchange", "total impressions", "total clicks", "total conversions", "total cost", "avg cpa", "avg ctr"))
}

# --- top 15 performing websites ---
cat("### Top 15 Performing Websites (by CPA, min ~14k impressions)\n")
top_apps |>
  format_app_table() |>
  print()

# --- bottom 15 performing websites ---
cat("### Bottom 15 Performing Websites (by CPA, min ~14k impressions)\n")
bottom_apps |>
  # re-sort descending for this table to show worst-at-top
  arrange(desc(avg_cpa)) |> 
  format_app_table() |>
  print()

# --- performance by ad exchange ---
cat("### Performance by Ad Exchange (Sorted by Conversions, then CPA)\n")
exchange_performance |>
  format_exchange_table() |>
  print()
```

## Analyze performance by type of device, creative size, creative message

```{r analyze device - data}
# analyze performance by the type of device (smartphone, pc, etc.)
device_performance <- dat_kpis |>
  group_by(device_make) |>
  summarise(
    total_impressions = sum(impressions),
    total_clicks = sum(clicks),
    total_conversions = sum(total_conversions),
    total_gross_cost = sum(gross_cost),
    # calculate overall cpa for the device type
    avg_cpa = ifelse(total_conversions > 0, total_gross_cost / total_conversions, na_real_),
    # calculate overall ctr for the device type
    avg_ctr = ifelse(total_impressions > 0, total_clicks / total_impressions, 0),
    # calculate overall conversion rate for the device type
    avg_conv_rate = ifelse(total_clicks > 0, total_conversions / total_clicks, 0),
    .groups = 'drop'
  )
```

```{r analyze device - kable, results='asis'}
# --- performance by device ---
cat("### Performance by Device\n")
device_performance |>
  mutate(
    total_impressions = scales::comma(total_impressions, accuracy = 1),
    total_clicks = scales::comma(total_clicks, accuracy = 1),
    total_conversions = scales::comma(total_conversions, accuracy = 1),
    total_gross_cost = scales::dollar(total_gross_cost, accuracy = 0.01),
    avg_cpa = scales::dollar(avg_cpa, accuracy = 0.01),
    avg_ctr = scales::percent(avg_ctr, accuracy = 0.01),
    avg_conv_rate = scales::percent(avg_conv_rate, accuracy = 0.01)
  ) |>
  kable(format = "html",
        col.names = c("device make", "total impressions", "total clicks", "total conversions", "total cost", "avg cpa", "avg ctr", "avg conv. rate")) |>
  print()
```

```{r analyze creative - data}
# analyze performance by ad size and the text message used

# performance by creative size 
size_performance <- dat_kpis |>
  group_by(creative_size) |>
  summarise(
    total_impressions = sum(impressions),
    total_clicks = sum(clicks),
    total_conversions = sum(total_conversions),
    total_gross_cost = sum(gross_cost),
    # calculate overall cpa for the creative size
    avg_cpa = ifelse(total_conversions > 0, total_gross_cost / total_conversions, na_real_),
    # calculate overall ctr for the creative size
    avg_ctr = ifelse(total_impressions > 0, total_clicks / total_impressions, 0),
    .groups = 'drop'
  ) |>
  # sort by number of impressions to see most used sizes first
  arrange(desc(total_impressions))

# performance by creative message
message_performance <- dat_kpis |>
  group_by(creative_messaging) |>
  summarise(
    total_impressions = sum(impressions),
    total_clicks = sum(clicks),
    total_conversions = sum(total_conversions),
    total_gross_cost = sum(gross_cost),
    # calculate overall cpa for the message
    avg_cpa = ifelse(total_conversions > 0, total_gross_cost / total_conversions, na_real_),
    # calculate overall conversion rate for the message
    avg_conv_rate = ifelse(total_clicks > 0, total_conversions / total_clicks, 0),
    .groups = 'drop'
  ) |>
  # sort by cost-effectiveness (lowest cpa)
  arrange(avg_cpa)
```

```{r analyze creative - kable, results='asis'}
# --- performance by creative size ---
cat("\n\n### Performance by Creative Size (Sorted by Impressions)\n")
size_performance |>
  mutate(
    total_impressions = scales::comma(total_impressions, accuracy = 1),
    total_clicks = scales::comma(total_clicks, accuracy = 1),
    total_conversions = scales::comma(total_conversions, accuracy = 1),
    total_gross_cost = scales::dollar(total_gross_cost, accuracy = 0.01),
    avg_cpa = scales::dollar(avg_cpa, accuracy = 0.01),
    avg_ctr = scales::percent(avg_ctr, accuracy = 0.01)
  ) |>
  kable(format = "html",
        col.names = c("creative size", "total impressions", "total clicks", "total conversions", "total cost", "avg cpa", "avg ctr")) |>
  print()

# --- performance by creative message ---
cat("\n\n### Performance by Creative Message (Sorted by CPA)\n")
message_performance |>
  mutate(
    total_impressions = scales::comma(total_impressions, accuracy = 1),
    total_clicks = scales::comma(total_clicks, accuracy = 1),
    total_conversions = scales::comma(total_conversions, accuracy = 1),
    total_gross_cost = scales::dollar(total_gross_cost, accuracy = 0.01),
    avg_cpa = scales::dollar(avg_cpa, accuracy = 0.01),
    avg_conv_rate = scales::percent(avg_conv_rate, accuracy = 0.01)
  ) |>
  kable(format = "html",
        col.names = c("creative messaging", "total impressions", "total clicks", "total conversions", "total cost", "avg cpa", "avg conv. rate")) |>
  print()
```


### EXPERIMENTAL
```{r find count of rows for each exchange, as well as summary of data}
# for counts, the simplest function is count()
# the 'sort = TRUE' argument shows the highest counts at the top

# Top 10 app_url counts
app_url_counts <- dat_kpis |>
  count(app_url, sort = TRUE)

# Top 10 exchange counts
exchange_counts <- dat_kpis |>
  count(exchange, sort = TRUE) 

# print the results
print("Top 10 App/URL Counts (by row count)")
print(app_url_counts)

print("Top 10 Exchange Counts (by row count)")
print(exchange_counts)
```


